aircore

### 2024-08-26 examples/README_nc.Rmd
vert plot

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/noaa-gml/rtorf)

[![R build
status](https://github.com/noaa-gml/rtorf/workflows/draft-pdf/badge.svg)](https://github.com/noaa-gml/rtorf/actions)

[![R-CMD-check](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml)

>>>>

![GitHub commit activity](https://img.shields.io/github/commit-activity/y/noaa-gml/rtorf)
[![R-CMD-check](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml)
![GitHub Repo stars](https://img.shields.io/github/stars/noaa-gml/rtorf)

### 2024-08-26 examples/aircore.Rmd
vert plot

Now we read the aircraft-pfp using the function `obs_read_nc`. To this date,
`solar_time` is not included for aircraft, so we `FALSE` that argument.

@@

>>>>

Now we read the `aircore` using the function `obs_read_nc`. To this date,
`solar_time` is not included for aircraft, so we `FALSE` that argument.

@@

```{r vertplot, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
x <- df3
x$ch4 <- x$value*1e+9
png("../man/figures/obsplot_aircore_vert.png", width = 1500, height = 1000, res = 200)
obs_plot(x, 
         time = "ch4", 
         y = "altitude_final", 
         colu = "month", n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
dev.off()
```

```{r obs_plot_vertt, fig.width=7, fig.height=5, eval = F}
x <- df3
x$ch4 <- x$value*1e+9obs_plot(x, 
         time = "ch4", 
         y = "altitude_final", 
         colu = "month", n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
```

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircore_vert.png?raw=true)
